Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-12 inst/examples/20160715-slides-Krakow.Rmd
ok
s

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "Singapore"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
---

@@

## Data: bibliographic catalogues 1640-1828

@@

### Methods: Open data analytical ecosystem

@@

### Preprocess & Enrich

@@

### Analyse & Visualize

@@

### 1. General trends & political events

@@

### 2. Publishers in Sweden and Turku

@@

### 3. Languages & religious texts in Finland

@@

### 4. University curriculum & Enlightenment in Finland

@@

### Thanks !

>>>>

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "Goettingen"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
---

@@

### Data: bibliographic catalogues 1640-1828

@@

## Methods: Open data analytical ecosystem

@@

## Preprocess & Enrich

@@

## Analyse & Visualize

@@

1. General trends & political events

@@

2. Publishers in Sweden and Turku

@@

3. Languages & religious texts in Finland

@@

4. University curriculum & Enlightenment in Finland

@@

##Thanks !
